quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-07 paper-quollr.Rmd
Updated the subsections

## Availability

@@

## Usage

@@

### Constructing the $2\text{-}D$ Model

@@

#### Scaling the data

@@

#### Computing hexagon grid configuration

@@

#### Binning the data

@@

##### Generating all possible centroids in a hexagonal grid

@@

##### Creating the coordinates of the hexagons

@@

##### Assigning data points to their respective hexagons

@@

##### Computing the standardized number of points within each hexagon

@@

##### Mapping the points to their corresponding hexagonal bins

@@

#### Obtaining bin centroids

@@

#### Indicating neighbors by line segments connecting centroids

@@

#### Identifying and removing low-density hexagons

@@

### Lifting the model into high dimensions

@@

### Prediction

@@

### Compute residuals and Root Within Bin Sum of Square (RWBSS)

@@

### Visualizations

@@

#### Hexagonal grid

@@

#### Triangular mesh

@@

#### \pD model visualization

@@

#### Link plots

@@

# Computational efficiency and optimization

@@

>>>>

# Usage

@@

@@

## Constructing the $2\text{-}D$ Model

@@

### Scaling the data

@@

### Computing hexagon grid configuration

@@

### Binning the data

@@

#### Generating all possible centroids in a hexagonal grid

@@

#### Creating the coordinates of the hexagons

@@

#### Assigning data points to their respective hexagons

@@

#### Computing the standardized number of points within each hexagon

@@

#### Mapping the points to their corresponding hexagonal bins

@@

### Obtaining bin centroids

@@

### Indicating neighbors by line segments connecting centroids

@@

### Identifying and removing low-density hexagons

@@

## Lifting the model into high dimensions

@@

## Prediction

@@

## Compute residuals and Root Within Bin Sum of Square (RWBSS)

@@

## Visualizations

@@

### Hexagonal grid

@@

### Triangular mesh

@@

### \pD model visualization

@@

### Link plots

@@

## Computational efficiency and optimization

@@

```{r}
df_exe_limb_int <- comb_all_data_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb, 
  model_highd = df_bin_limb, 
  model_2d = df_bin_centroids_limb
)
```

```{r tsne-link-limb, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right)."}

tsne_link_limb <- show_link_plots(
  point_data = df_exe_limb_int, 
  edge_data = trimesh_data_limb, 
  point_colour = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494')
)

class(tsne_link_limb) <- c(class(tsne_link_limb), "htmlwidget")

tsne_link_limb
```

```{r}
df_exe_limb_int_best <- comb_all_data_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb2, 
  model_highd = df_bin_limb, 
  model_2d = df_bin_centroids_limb
)
```

```{r tsne-link-limb-best, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right)."}

tsne_link_limb_best <- show_link_plots(
  point_data = df_exe_limb_int_best, 
  edge_data = trimesh_data_limb, 
  point_colour = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494')
)

class(tsne_link_limb_best) <- c(class(tsne_link_limb_best), "htmlwidget")

tsne_link_limb_best
```

### 2025-10-07 paper-quollr.tex
Updated the subsections

\subsection{Availability}\label{availability}

@@

\subsection{Usage}\label{usage}

@@

\subsubsection{Main function}\label{main-function}

@@

\subsubsection{\texorpdfstring{Constructing the \(2\text{-}D\) Model}{Constructing the 2\textbackslash text\{-\}D Model}}\label{constructing-the-2text-d-model}

@@

\paragraph{Scaling the data}\label{scaling-the-data}

@@

\paragraph{Computing hexagon grid configuration}\label{computing-hexagon-grid-configuration}

@@

\paragraph{Binning the data}\label{binning-the-data}

@@

\subparagraph{Generating all possible centroids in a hexagonal grid}\label{generating-all-possible-centroids-in-a-hexagonal-grid}

@@

\subparagraph{Creating the coordinates of the hexagons}\label{creating-the-coordinates-of-the-hexagons}

@@

\subparagraph{Assigning data points to their respective hexagons}\label{assigning-data-points-to-their-respective-hexagons}

@@

\subparagraph{Computing the standardized number of points within each hexagon}\label{computing-the-standardized-number-of-points-within-each-hexagon}

@@

\subparagraph{Mapping the points to their corresponding hexagonal bins}\label{mapping-the-points-to-their-corresponding-hexagonal-bins}

@@

\paragraph{Obtaining bin centroids}\label{obtaining-bin-centroids}

@@

\paragraph{Indicating neighbors by line segments connecting centroids}\label{indicating-neighbors-by-line-segments-connecting-centroids}

@@

\paragraph{Identifying and removing low-density hexagons}\label{identifying-and-removing-low-density-hexagons}

@@

\subsubsection{Lifting the model into high dimensions}\label{lifting-the-model-into-high-dimensions}

@@

\subsubsection{Prediction}\label{prediction}

@@

\subsubsection{Compute residuals and Root Within Bin Sum of Square (RWBSS)}\label{compute-residuals-and-root-within-bin-sum-of-square-rwbss}

@@

\subsubsection{Visualizations}\label{visualizations}

@@

\paragraph{Hexagonal grid}\label{hexagonal-grid}

@@

\paragraph{Triangular mesh}\label{triangular-mesh}

@@

\paragraph{\texorpdfstring{$p\text{-}D$ model visualization}{model visualization}}\label{model-visualization}

@@

\paragraph{Link plots}\label{link-plots}

@@

\section{Computational efficiency and optimization}\label{computational-efficiency-and-optimization}

>>>>

\section{Usage}\label{usage}

@@

@@

\subsection{Main function}\label{main-function}

@@

\subsection{\texorpdfstring{Constructing the \(2\text{-}D\) Model}{Constructing the 2\textbackslash text\{-\}D Model}}\label{constructing-the-2text-d-model}

@@

\subsubsection{Scaling the data}\label{scaling-the-data}

@@

\subsubsection{Computing hexagon grid configuration}\label{computing-hexagon-grid-configuration}

@@

\subsubsection{Binning the data}\label{binning-the-data}

@@

\paragraph{Generating all possible centroids in a hexagonal grid}\label{generating-all-possible-centroids-in-a-hexagonal-grid}

@@

\paragraph{Creating the coordinates of the hexagons}\label{creating-the-coordinates-of-the-hexagons}

@@

\paragraph{Assigning data points to their respective hexagons}\label{assigning-data-points-to-their-respective-hexagons}

@@

\paragraph{Computing the standardized number of points within each hexagon}\label{computing-the-standardized-number-of-points-within-each-hexagon}

@@

\paragraph{Mapping the points to their corresponding hexagonal bins}\label{mapping-the-points-to-their-corresponding-hexagonal-bins}

@@

\subsubsection{Obtaining bin centroids}\label{obtaining-bin-centroids}

@@

\subsubsection{Indicating neighbors by line segments connecting centroids}\label{indicating-neighbors-by-line-segments-connecting-centroids}

@@

\subsubsection{Identifying and removing low-density hexagons}\label{identifying-and-removing-low-density-hexagons}

@@

\subsection{Lifting the model into high dimensions}\label{lifting-the-model-into-high-dimensions}

@@

\subsection{Prediction}\label{prediction}

@@

\subsection{Compute residuals and Root Within Bin Sum of Square (RWBSS)}\label{compute-residuals-and-root-within-bin-sum-of-square-rwbss}

@@

\subsection{Visualizations}\label{visualizations}

@@

\subsubsection{Hexagonal grid}\label{hexagonal-grid}

@@

\subsubsection{Triangular mesh}\label{triangular-mesh}

@@

\subsubsection{\texorpdfstring{$p\text{-}D$ model visualization}{model visualization}}\label{model-visualization}

@@

\subsubsection{Link plots}\label{link-plots}

@@

\subsection{Computational efficiency and optimization}\label{computational-efficiency-and-optimization}
